---
title: "hw3"
author: "Caroline Shepherd"
date: "5/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# attach packages
library(tidyverse)
library(here)
library(ggplot2)
library(janitor)
library(rootSolve)

```

```{r}
# Read in the data and clean it

carbon <- read_csv(here("HW3_data.csv")) %>% 
  clean_names() %>% 
  rename(price = price_cents,
         q_low = q_low_kwh,
         q_high = q_high_kwh)
```

```{r}
# Create and plot the marginal demand of High and Low income groups and estimate a linear regression model
  
# High
high_lm <- lm(price ~ q_high, data = carbon)
summary(high_lm)

# Low
low_lm <- lm(price ~ q_low, data = carbon)
summary(low_lm)

# need to rearrange the parameter to get Q(P)! 

# Qgg = Qlow(P) + Qlow(h) 

# Importantly, since they-intercepts are different, we know that Qagg(P) will have a kink. I include an ifelse() statement to take
# care of the kink.

# define a function to get demand

demand <- function(p, model){
  q <- (p - model$coefficients[[1]])/model$coefficients[[2]]
  q <- ifelse(q<0,0,q)
  return(q)
}

# for each p level, return estimated aggregate demand
demand_agg <- function(p){
  q <- demand(p, low_lm) + demand(p, high_lm)
  return(q)
}

price = seq(0, 30, length.out = 100)
Qagg <- map(price, demand_agg) %>% 
  unlist()

df<- tibble(Qagg = Qagg, price = price)

ggplot(df, aes(Qagg, price)) +
  geom_line() +
  geom_text(aes(x = 2e+05, y = 5),
            label = "Aggregate Monthly Demand Curve") +
  labs(x = "Quantity in kWh",
       y = "Price")

# I also define functions for calculating the consumer surplus:

CS <- function(p, model){
  q <- demand(p, model)
  cs <- 0.5*(model$coefficients[[1]] - p)*q
  return(cs)
}

CS_agg <- function(p){
  cs <- CS(p,model_demand_l) + CS(p,model_demand_h)
  return(cs)
}

```


### Demand Equations

# Low Income Demand:
lowMWTP = `r low_lm$coefficients[1]` + `r low_lm$coefficients[2]` * q

# High Income Demand:
highMWTP = `r high_lm$coefficients[1]` + `r high_lm$coefficients[2]` * q

# Agg demand equation:

```{r}
# Aggregate demand: sum horizontally

agg <- predict_demand_p %>%
  mutate(q_agg = ifelse(is.na(low_q), high_q, low_q + high_q))

# Easy function for q

agg_q_fun <- function(p){
  agg_q <- ((p - high_lm$coefficients["(Intercept)"]) / high_lm$coefficients["q_high"]) + ((p - low_lm$coefficients["(Intercept)"]) / low_lm$coefficients["q_low"])
  return(agg_q)
}

dmd_sq_agg_q <- agg_q_fun(3)
predict_agg_demand <- data.frame(p = p_vector) %>%
  mutate(q = agg_q_fun(p)) %>%
  filter(p <= 10)
agg_lm <- lm(p ~ q, data = predict_agg_demand)
agg_p_fun <- function(q){
  p <- agg_lm$coefficients["(Intercept)"] + agg_lm$coefficients["q"] * q
  return(p)
}

```

### Aggregate Demand Equation

q = ((p - `r high_lm$coefficients["(Intercept)"]` ) / `r high_lm$coefficients["q_high"]` ) + ((p - `r low_lm$coefficients["(Intercept)"]` ) / `r low_lm$coefficients["q_low"]` )

p = `r agg_lm$coefficients["(Intercept)"]` + `r agg_lm$coefficients["q"]` * q


```{r}
# P Function low
funct_low_p <- function(q){
  predicted_p_low <- low_lm$coefficients["(Intercept)"] + low_lm$coefficients["q_low"] * q
  return(predicted_p_low)
}
# q function low
funct_low_q <- function(p){
  predicted_q_low <- (p - low_lm$coefficients["(Intercept)"]) / low_lm$coefficients["q_low"]
  return(predicted_q_low)
}
# x intercept low income
xint_low_p <- (0 - low_lm$coefficients["(Intercept)"]) / low_lm$coefficients["q_low"]
```


